Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-08-30 paper/ms.tex
new results section

The main purpose of this section is to show how different
observational constraints narrow down the parameters space of allowed
models. Each sub-sections presents the effect of adding new pieces of
observational or statistical evidence.

@@

In Figure \ref{fig:halos} we present the results for  the
integrated dark matter halo surface density as a function of halo
mass. Each line corresponds to one of the 210 sub-volumes in the
Bolshoi simulation. The gray band indicates the surface density
values for LAEs allowed reported in observations \citep{Yamada2012}.

This result provides the basis to understand why only a specific range of models
${\mathcal M}$ can be expected to be consistent with
observations. From Figure \ref{fig:halos} we can read that models with
a minimum mass $\log_{10} M_{\rm min}>11.5$\hMsun will always have a
surface number density lower than the observational
constrain. This makes impossible that models in that range can be
compatible with observations, there are simply to few halos compared
to observed LAEs.

The opposite is true in models with $\log_{10} M_{\rm min}<10.5$ that
have a surface number density larger than observations. In those cases
the occupation fraction $f_{\rm occ}<1.0$ can be tuned in order to
lower the halo number density to match observations.

Figure \ref{fig:halos} also illustrates the impact of cosmic
variance. At fixed mass there is an scatter of $0.3-0.6$ dex in the
mass range $10^{10}\hMsun < M_{\rm  min}<10^{11}\hMsun$.  A consequence of
this variation is that models with the same mass range and occupation
fraction can have mock fields with number densities varying up to a
factor of $\sim 2-5$. Also, the scatter in mocks across the simulation
is comparable to the $0.3$ dex scatter in observations.

In the same Figure \ref{fig:halos} we see that at fixed number
density, around the range allowed by observations, there is an scatter
in the masses of $0.4-0.5$ dex. This intrinsic scatter in the masses
with a given number density adds is also included in the mock
construction process, enlarging the range of possible models
consistent with observations.

@@

Figure \ref{fig:landscape} presents regions in parameter space $M_{\rm
min}-M_{\rm max}$, $M_{\rm min}-f_{\rm occ}$ where the KS test yields
values of $P>0.05$ at least for one mock survey, which is the most
conservative assumption for agreement between a model and observations. For those models it
is not possible reject the hypothesis that the simulated and observed
data for the surface number density come from the same parent
distribution. In total, there are between $550$ to $600$ models out of
the original $9000$ models that have at least one mock survey
consistent with observations. By inspection of Figure
\ref{fig:landscape} we see that the halo number abundance is able to
constraint the minimum mass $M_{\rm min}$ to a narrow range, while
$M_{\rm max}$ and $f_{\rm occ}$ remain unconstrained.

In Figure \ref{fig:landscape} there are three regions of parameter
space that can be clearly distinguished. The first region corresponds
to models where the minimum mass is high $\log_{10}M_{\rm min}>
11.5$. None of these models is compatible with observations as expected
from the arguments presented in the previous subsection. For these
models the number density of LAEs is too low compared to
observations.

The second region corresponds to an intermediate range for the minimum
mass $10.5<\log_{10}M_{\rm min}<11.5$ where, regardless of the value of
the maximum mass $M_{\rm max}$, it is possible to tune the occupation
fraction $f_{\rm occ}$ to bring some of the mock observations into
good agreement with observations. In this region of parameter space
one can find two extreme kinds of models.  One kind where the
mass interval $\Delta M\equiv \log_{10} M_{\rm max} - \log_{10}M_{\rm
  min}$ is narrow with $\Delta M<1.0$ dex, others where the mass interval is 
extended $\Delta M>1.0$dex going up to the maximum halo mass
present in the simulation at that redshift, up to $\Delta M = 2.5$ dex
in some cases.

The third region in parameter space corresponds to $\log_{10}M_{\rm
  min}<10.5$. In this case only models with a very narrow mass interval of
at most $0.5$ dex ($\log_{10}M_{\rm max}<11.0$) and low
occupation fractions $f_{\rm occ}<0.3$ are allowed.

@@

However, the additional information we gain with this test is the
relative abundance of models in the parameter space. Not all the
models in the second region have an equal abundance. By inspection of
Figure \ref{fig:landscape} it seems that models with $\log_{10}M_{\rm
  min}\sim 10^{11.3}$\hMsun and low occupation fraction $f_{\rm}<0.3$
are preferred.  In the next sub-section we explore in detail the
models in this region, imposing tighter constraints on the KS test
results and exploring the mocks' consistency with the angular correlation
function.

@@

In the previous Section we present a conservative criterion of
agreement by selecting the models that had at least one mock survey
with $P>0.05$ in the KS test. Now we turn to a more strict selection
by requiring all constructed mock surveys to be consistent with
observations.

@@

Figure \ref{fig:restriction_mock} presents the locii of these models
in the parameter space $M_{\rm min}-M_{\rm max}$ and $M_{\rm
  min}-f_{\rm occ}$. With this constraints the
number of consistent models with  $10.5 < \log_{10}M_{\rm min}< 11.0$ are
greatly reduced. This corresponds to the regions in the parameter
space in Figure \ref{fig:landscape} that already had a low number of
consistent mock surveys. On the other hand, from the right panel in
Figure \ref{fig:restriction_mock} one can see that there is not a
strong reduction on the favored values for the occupation fraction
$f_{\rm occ}$.

@@

Figure \ref{fig:correlation_parameters} shows the main results in a
$\theta_{0}-\beta$  plane where the average and standard deviation
over the mocks is shown in comparison with the result derived from
observations.  The error bars in this Figure represents the standard
deviation of the ACF over all the 15 mock fields used to make the
computation.  These error bars are larger than the statistical
uncertainty from the fitting procedure on a single field.

In the left panel Figure \ref{figure:correlation_parameters} we see
how the observational ACF measured by \cite{Hayashino2004} (green dot)
is successful in reducing the total number of possible models. Only
those with angular-correlation length within
$15^{\prime\prime}<\theta_{0}<23^{\prime\prime}$ are considered to
reproduce observations. The right panel of Figure
\ref{figure:correlation_parameters} shows the results for fields in
the mock catalog that have an average number density that are compared
against the fit of the data reported by \cite{Ouchi2010}. In this case
we find that there are large uncertainties in the observational data,
however it is possible to discard a fraction of the models.

In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
models in the planes $M_{\rm min}-M_{\rm  max}$ and $M_{\rm min}-f_{\rm occ}$
both for the comparisong against \cite{Hayashino2004} and
\cite{Ouchi2010}. To make this selection we consider that
a model is consistent with observations if there is a $1-\sigma$
overlap between both the correlation length $\theta_0$ and the power
$\beta$. We clearly see from this Figure that the conditions imposed
by \cite{Hayashino2004} are the tightest. Comparing this Figure with
the results shown in Figure \ref{fig:restriction_mock} we see that
practically all models with $M_{\rm max}>10^{12}$ are removed. On the
other hand the comparison against \cite{Ouchi2010} does not
substantially reduce the number of models.

At this point we take the most strict selection criterio and keep the
models that are consistent with both observational constraints. This
basically reduces the selection to the models already restricted by
the data in \cite{Hayashino2004} as presented in the lower panels of Figure
\ref{fig:restriction_mock_and_f_occ_corr}. Our main conclusions after
this comparison is that clustering information is able to put
meaningful constraints on the values of $M_{\rm max}$. However, the
possible values for the occupation fraction are still in the initial
range $0.1\leq f_{\rm occ}\leq 1$.

>>>>

The main purpose of this section is to show how different
observational constraints narrow down the parameters space of allowed
models. Each sub-section presents the effect of adding new pieces of
observational or statistical evidence.

@@

In Figure \ref{fig:halos} we present the results for  the
integrated dark matter halo surface density as a function of the
minimum halo mass $M_{\rm min}$. Each line corresponds to one of the
210 sub-volumes in the Bolshoi simulation. The gray band indicates the
surface density values for LAEs allowed by observations
\citep{Yamada2012}.

This result allows us to understand why only a specific range of
models ${\mathcal M}$ can be expected to be consistent with
observations. From Figure \ref{fig:halos} we can read that models with
a minimum mass $M_{\rm min}>10^{11.5}$\hMsun will always have a
surface number density lower than the observational constrain. This
makes impossible that models in that range can be compatible with
observations, there are simply to few halos compared to observed
LAEs. The opposite is true in models with $M_{\rm
  min}<10^{10.5}$\hMsun that have a surface number density larger
observations. In those cases the occupation fraction $f_{\rm occ}<1.0$
can be tuned in order to lower the halo number density to match
observations.

Figure \ref{fig:halos} also illustrates the impact of cosmic
variance. At fixed mass there is an scatter of $0.3-0.6$ dex in the
number density abudance.  A consequence of this variation is that
models with the same mass range and occupation fraction can have mock
fields with number densities varying up to a factor of $\sim
2-5$. This scatter is comparable to the $0.3$ dex scatter coming from 
observations. In the same Figure \ref{fig:halos} we see that at fixed
number density, around the range allowed by observations, there is an
scatter in the masses of $0.4-0.5$ dex.

This scatter induced by cosmic variance is naturally included in the
mock construction process. This will allows us to have a wider range
of models compatible with observations, as compared with a model that
neglects cosmic variance.

@@

Figure \ref{fig:landscape} presents regions in parameter space $M_{\rm
min}$-$M_{\rm max}$, $M_{\rm min}$-$f_{\rm occ}$ where the KS test yields
values of $P>0.05$ at least for one mock survey, which is the most
conservative assumption for agreement between a model and observations. For those models it
is not possible reject the hypothesis that the simulated and observed
data for the surface number density come from the same parent
distribution. In total, there are between $550$ to $600$ models out of
the original $9000$ models that have at least one mock survey
consistent with observations. By inspection of Figure
\ref{fig:landscape} we see that the halo number abundance is able to
constraint the minimum mass $M_{\rm min}$ to a narrow range, while
$M_{\rm max}$ and $f_{\rm occ}$ remain largely unconstrained.

In Figure \ref{fig:landscape} there are three regions of parameter
space that can be clearly distinguished. The first corresponds to
models where the minimum mass is high $M_{\rm min}>
10^{11.5}\hMsun$. None of these models is compatible with observations
as expected from the arguments presented in the previous
subsection. For these models the number density of LAEs is too low
compared to observations.

The second region corresponds to an intermediate range for the minimum
mass $10^{10.5}\hMsun < M_{\rm min}< 10^{11.5}\hMsun$ where,
regardless of the value of the maximum mass $M_{\rm max}$, it is
possible to tune the occupation fraction $f_{\rm occ}$ to bring some
of the mock surveys into good agreement with observations. In this
region of parameter space one can find two extreme kinds of models.
One kind where the mass interval $\Delta M\equiv \log_{10} M_{\rm max}
- \log_{10}M_{\rm  min}$ is narrow with $\Delta M<1.0$ dex, others
where the mass interval is  extended $\Delta M>1.0$ dex going up to
the maximum halo mass present in the simulation at that redshift, with
$\Delta M = 2.5$ dex in those cases.

The third region in parameter space corresponds to $M_{\rm
  min}<10^{10.5}\hMsun$. In this case only models with a very narrow
mass interval of at most $0.5$ dex ($M_{\rm max}<10^{11.0}\hMsun$) and low
occupation fractions $f_{\rm occ}\leq 0.3$ are allowed.

@@

However, the additional information we gain with this test is the
relative abundance of models in the parameter space. Not all 
models in the second region have an equal abundance. By inspection of
Figure \ref{fig:landscape} it seems that models with $\log_{10}M_{\rm
  min}\sim 10^{11.3}$\hMsun and low occupation fraction $f_{\rm}\leq 0.3$
are preferred.  In the next sub-sections we explore in detail the
models in this region, imposing tighter constraints on the KS test
results and exploring the mocks' consistency with the angular correlation
function.

@@

In the previous sub-section we presented a conservative criterion of
agreement by selecting the models that had at least one mock survey
with $P>0.05$ in the KS test. Now we turn to a more strict selection
by requiring all constructed mock surveys to be consistent with
observations.

@@

Figure \ref{fig:restriction_mock} presents the locii of these models
in the parameter space $M_{\rm min}-M_{\rm max}$ and $M_{\rm
  min}-f_{\rm occ}$. With this constraints the
number of consistent models with  $10.5 < \log_{10}M_{\rm min}< 11.0$ are
greatly reduced. This corresponds to the regions in the parameter
space in Figure \ref{fig:landscape} that already had a low number of
consistent mock surveys. On the other hand, from the right panel in
Figure \ref{fig:restriction_mock} one can see that the reduction of
favored values for the occupation fraction $f_{\rm occ}$ is not strong.

@@

Figure \ref{fig:correlation_parameters} shows the main results in a
$\theta_{0}-\beta$  plane where the average and standard deviation
over the mocks is shown in comparison with the result derived from
observations. In the left panel Figure \ref{fig:correlation_parameters} we see
how the observational ACF measured by \cite{Hayashino2004} 
can be successful in reducing the total number of possible models. The
right panel shows the results for fields in the mock catalog with an
average number density compared against the fit of the data
reported by \cite{Ouchi2010}. In this case we find that there are
large uncertainties coming from the observational data, and only a reduced
fraction of the modesl can be discartded.

In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
models in the planes $M_{\rm min}$-$M_{\rm  max}$ and $M_{\rm min}$-$f_{\rm occ}$
both for the comparisons against \cite{Hayashino2004} and
\cite{Ouchi2010}. To make this selection we consider that
a model is consistent with observations if there is a $1$-$\sigma$
overlap between both the correlation length $\theta_0$ and the power
$\beta$. We clearly see from this Figure that the conditions imposed
by \cite{Hayashino2004} are the tightest. Comparing this Figure with
the results shown in Figure \ref{fig:restriction_mock} we see that
practically all models with $M_{\rm max}>10^{12}$ are removed. On the
other hand the comparison against \cite{Ouchi2010} does not
substantially reduce the number of models.

At this point we take the most strict decision to keep 
models consistent with both observational constraints. This
reduces the selection to the models already restricted by
the data in \cite{Hayashino2004} as presented in the lower panels of Figure
\ref{fig:restriction_mock_and_f_occ_corr}. Our main conclusions after
this comparison is that clustering information is able to put
meaningful constraints on the values of $M_{\rm max}$. However, the
possible values for the occupation fraction, despite having a strong correlation
with $M_{\rm min}$, still are in the initial range $0.1\leq f_{\rm
  occ}\leq 1$.
